---
title: "logistic_regression"
date: '2021-04-26 (updated: `r Sys.Date()`)'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

```{r echo=FALSE}
library(tidyverse)
library(broom)
library(sjPlot)
library(ggpubr)
options(digits = 7)
```

```{r}
df <-
  read_csv("data/option_discussed.csv") %>%
  mutate(
    category_remember = category_remember %>% fct_relevel(ref = 'all'),
    category_remember2 = category_remember %>% fct_relevel(ref = 'implant'),
    category_remember3 = category_remember %>% fct_relevel(ref = 'tissue')
  )
```

```{r}
glimpse(df)
```

## Descriptive statistics
### Overall
```{r}
nT <- nrow(df)

df %>% 
  dplyr::select(
    age,
    asir_composite,
    bmi,
    body_image_scale_score,
    bsi_global_score, 
    category_remember) %>% 
  group_by(category_remember) %>% 
  summarise(n=n(), 
            percent=n()/nT*100)
```

```{r}
df %>% 
  group_by(race) %>% 
  summarise(n=n(), percent=n()/nT*100) %>% 
  arrange(percent %>% desc())
```

```{r}
df %>% 
  group_by(ethnicity) %>%
  summarise(n=n(), percent=n()/nT*100) %>% 
  arrange(percent %>% desc())
```

```{r}
df %>%
  summarise(across(
    c(
      bmi,
      age,
      asir_composite,
      body_image_scale_score,
      bsi_global_score
    ),
    list(
      mean = mean,
      sd = sd,
      median = median,
      IQR = IQR
    )
  )) %>% t()
```

### 3 categories
```{r}
df %>%
  group_by(category_remember) %>%
  summarise(across(
    c(
      bmi,
      age,
      asir_composite,
      body_image_scale_score,
      bsi_global_score
    ),
    list(
      mean = mean,
      sd = sd,
      median = median,
      IQR = IQR
    )
  )) %>% t()
```

```{r}
df %>% 
  group_by(category_remember, race) %>% 
  summarise(n=n(), percent=n()/nT*100)
```

```{r}
df %>% 
  group_by(category_remember, ethnicity) %>% 
  summarise(n=n(), percent=n()/nT*100)
```

## KW, Dunn test
```{r}
library(FSA)
```

### BMI
#### kruskal.test
```{r}
# bmi is significant
kruskal.test(bmi ~ category_remember, df)
plot_color <- c("#00AFBB", "#E7B800", "#FC4E07")

ggboxplot(
  df,
  x = "category_remember",
  y = "bmi",
  palette = plot_color,
  fill = "category_remember",
  xlab = "Remember options discussed",
  ylab = "BMI"
) + rremove("legend")

dunnTest(bmi ~ category_remember, df)
```

#### Normality check
```{r}
norm_check <- function(x) {
  shapiro.test(x) %>% print()
  hist(x)
  qqnorm(x)
  qqline(x)  
}

norm_check(df$bmi)
```

### age
#### kruskal.test
```{r}
kruskal.test(age ~ category_remember, df)

ggboxplot(
  df,
  x = "category_remember",
  y = "age",
  palette = plot_color,
  fill = "category_remember",
  xlab = "Remember options discussed",
  ylab = "Age"
) + rremove("legend")
```

#### Normality check
```{r}
norm_check(df$age)
```

### ASIR
#### kruskal.test
```{r}
# ASIR is slightly significant
kruskal.test(asir_composite ~ category_remember, df)

ggboxplot(
  df,
  x = "category_remember",
  y = "asir_composite",
  palette = plot_color,
  fill = "category_remember",
  xlab = "Remember options discussed",
  ylab = "ASI-R Composite"
) + rremove("legend")

dunnTest(asir_composite ~ category_remember, df)
```

#### Normality check
```{r}
norm_check(df$asir_composite)
```

#### ANOVA
```{r}
aov(asir_composite ~ category_remember, df) %>% summary()
```

```{r}
TukeyHSD(aov(asir_composite ~ category_remember, df))
```

```{r}
DescTools::ScheffeTest(aov(asir_composite ~ category_remember, df))
```

### BIS
#### kruskal.test
```{r}
# BIS is significant, interesting
kruskal.test(body_image_scale_score ~ category_remember, df)

ggboxplot(
  df,
  x = "category_remember",
  y = "body_image_scale_score",
  palette = plot_color,
  fill = "category_remember",
  xlab = "Remember options discussed",
  ylab = "BIS"
) + rremove("legend")

dunnTest(body_image_scale_score ~ category_remember, df)
```

#### Normality check
```{r}
norm_check(df$body_image_scale_score)
```

### BSI global
#### kruskal.test
```{r}
# bsi_global_score is slightly significant
kruskal.test(bsi_global_score ~ category_remember, df)

ggboxplot(
  df,
  x = "category_remember",
  y = "bsi_global_score",
  palette = plot_color,
  fill = "category_remember",
  xlab = "Remember options discussed",
  ylab = "BSI Global"
) + rremove("legend")

dunnTest(bsi_global_score ~ category_remember, df)
```

#### Normality check
```{r}
norm_check(df$bsi_global_score)
```

## Uni logit
```{r}
library(nnet)
library(broom)
library(MASS)
```

### reference: all
```{r}
tab_model(
  multinom(category_remember ~ bmi, df),
  multinom(category_remember ~ age, df),
  multinom(category_remember ~ asir_composite, df),
  multinom(category_remember ~ body_image_scale_score, df),
  multinom(category_remember ~ bsi_global_score, df),
  show.reflvl = TRUE
)
```

#### Type III
```{r}
multinom(category_remember ~ bmi, df) %>% 
  car::Anova(type = 3)
multinom(category_remember ~ age, df) %>% 
  car::Anova(type = 3)
multinom(category_remember ~ asir_composite, df) %>% 
  car::Anova(type = 3)
multinom(category_remember ~ body_image_scale_score, df) %>% 
  car::Anova(type = 3)
multinom(category_remember ~ bsi_global_score, df) %>% 
  car::Anova(type = 3)
```

### reference: implant
```{r}
tab_model(
  multinom(category_remember2 ~ bmi, df),
  multinom(category_remember2 ~ age, df),
  multinom(category_remember2 ~ asir_composite, df),
  multinom(category_remember2 ~ body_image_scale_score, df),
  multinom(category_remember2 ~ bsi_global_score, df),
  show.reflvl = TRUE
)
```

### reference: tissue
```{r}
tab_model(
  multinom(category_remember3 ~ bmi, df),
  multinom(category_remember3 ~ age, df),
  multinom(category_remember3 ~ asir_composite, df),
  multinom(category_remember3 ~ body_image_scale_score, df),
  multinom(category_remember3 ~ bsi_global_score, df),
  show.reflvl = TRUE
)
```

## Multinomial logistic regression
### reference: all
```{r message=FALSE, warning=FALSE, include=FALSE}
full_mdl <- 
  multinom(category_remember ~ asir_composite + bmi + body_image_scale_score + bsi_global_score, df)
```

- Full model

```{r}
tab_model(full_mdl, show.reflvl = TRUE)
```

```{r include=FALSE}
step_mdl <- stepAIC(full_mdl, direction = "backward", trace = 0)
```

#### Type III
```{r}
step_mdl %>% car::Anova(type = 3)
```

- selected model

```{r}
tab_model(step_mdl, show.reflvl = TRUE)
```

### reference: implant
```{r include=FALSE}
full_mdl_ref_implant <- 
  multinom(category_remember2 ~ asir_composite + bmi + body_image_scale_score + bsi_global_score, df)
```

- Full model

```{r}
tab_model(full_mdl_ref_implant, show.reflvl = TRUE)
```

```{r include=FALSE}
step_mdl_ref_implant <- stepAIC(full_mdl_ref_implant, direction = "backward", trace = 0)
```

- Selected model

```{r}
tab_model(step_mdl_ref_implant, show.reflvl = TRUE)
```

### reference: tissue
```{r}
full_mdl_ref_tissue <- 
  multinom(category_remember3 ~ asir_composite + bmi + body_image_scale_score + bsi_global_score, df)
```

- Full model

```{r}
tab_model(full_mdl_ref_tissue, show.reflvl = TRUE)
```

```{r include=FALSE}
step_mdl_ref_tissue <- stepAIC(full_mdl_ref_tissue, direction = "backward", trace = 0)
```

- Selected model
```{r}
tab_model(step_mdl_ref_tissue, show.reflvl = TRUE)
```